Robust Control of a Fluxonium Qubit

### 2020-11-28 paper/3fluxonium.tex
unlimited powah

The optimization problem takes the form:
\begin{mini!}[2]
  {x_{0:N}, u_{0:N\text{-}1}}{\sum_{k=1}^N \norm{x_k\text{-}x_f}_{Q_k}
    + \sum_{k=1}^{N-1} \norm{u_k}_{R_k}}{}{} \label{eq:costfun}
    \addConstraint{x_{k+1}}{= f(x_k, u_k)}  \label{eq:dyn_con}
    \addConstraint{(x_1, x_N \; \textrm{given})}
    \addConstraint{g_k(x_k,u_k)}{\leq 0}
    \addConstraint{h_k(x_k,u_k)}{=0}
\end{mini!}
where the augmented state and controls are given by:
\begin{equation}
  x = \begin{bmatrix} \psi^{(1)} \\ \psi^{(2)} \\ \int a \ dt\\ a \\ \pdv*{a}{t} \end{bmatrix} \quad
  u = \begin{bmatrix} \pdv*[2]{a}{t} \end{bmatrix}
  \label{eq:astatecontrols}
\end{equation}
The initial and final conditions are determined by the
desired gate, which requires two quantum states
to specify $\psi^{(1)}$, $\psi^{(2)}$.
The ALTRO implementation we use does not currently support complex numbers so
we compute in the isomorphism $\mathcal{H}(\mathbb{R}^{2n}) \cong \mathcal{H}(\mathbb{C}^{n})$
given in \cite{leung2017speedup}:
\begin{equation}
  H \psi \cong \begin{bmatrix} H_{\textrm{re}} & -H_{\textrm{im}} \\ H_{\textrm{im}} & H_{\textrm{re}}\end{bmatrix}
  \begin{bmatrix} \psi_{\textrm{re}} \\ \psi_{\textrm{im}}\end{bmatrix}
  \label{eq:isomorphism}
\end{equation}
The discrete dynamics function \eqref{eq:dyn_con} integrates the TDSE dynamics for the quantum states
using \eqref{eq:tdse} and \eqref{eq:hamiltonian}
and integrates the moments of the flux drive amplitude. Exposing lower order moments of the flux
drive amplitude allows us to penalize their norms, smoothing the flux drive amplitude
and mitigating AWG ringing due to high frequency transitions.
The matrices $Q_{k}$ and $R_{k}$ define the penalty metric.
Including objectives at each knot point smoothens the optimization landscape, though
the importance of the final state objective is encoded in the relative
weight $Q_{N} \sim N \cdot Q_{k}$.
We choose $Q$ to be diagonal because it is computationally efficient. This corresponds
to penalizing phase differences between the quantum states, although
other phase-insensitive metrics such as infidelity may be employed.

>>>>

The optimization problem takes the form:
\begin{mini!}[2]
  {x_{0:N}, u_{0:N\text{-}1}}{\sum_{k=1}^N \norm{x_k\text{-}x_f}_{Q_k}
    + \sum_{k=1}^{N-1} \norm{u_k}_{R_k}}{}{} \label{eq:costfun}
    \addConstraint{x_{k+1}}{= f(x_k, u_k)}  \label{eq:dyn_con}
    \addConstraint{(x_1, x_N \; \textrm{given})}
    \addConstraint{g_k(x_k,u_k)}{\leq 0}
    \addConstraint{h_k(x_k,u_k)}{=0}
\end{mini!}
where the augmented state and controls are given by:
\begin{equation}
  x = \begin{bmatrix} \psi^{(1)} \\ \psi^{(2)} \\ \int a \ dt\\ a \\ \pdv*{a}{t} \end{bmatrix} \quad
  u = \begin{bmatrix} \pdv*[2]{a}{t} \end{bmatrix}
  \label{eq:astatecontrols}
\end{equation}
The initial and final conditions are determined by the
desired gate, which requires two quantum states
to specify $\psi^{(1)}$, $\psi^{(2)}$.
The ALTRO implementation we use does not currently support complex numbers so
we compute in the isomorphism $\mathcal{H}(\mathbb{R}^{2n}) \cong \mathcal{H}(\mathbb{C}^{n})$
given in \cite{leung2017speedup}:
\begin{equation}
  H \psi \cong \begin{bmatrix} H_{\textrm{re}} & -H_{\textrm{im}} \\ H_{\textrm{im}} & H_{\textrm{re}}\end{bmatrix}
  \begin{bmatrix} \psi_{\textrm{re}} \\ \psi_{\textrm{im}}\end{bmatrix}
  \label{eq:isomorphism}
\end{equation}
The discrete dynamics function \eqref{eq:dyn_con} integrates the TDSE dynamics for the quantum states
using \eqref{eq:tdse} and \eqref{eq:hamiltonian}
and integrates the moments of the flux drive amplitude. Exposing lower order moments of the flux
drive amplitude allows us to penalize their norms in \eqref{eq:costfun}, smoothing the flux drive amplitude
and mitigating AWG ringing due to high frequency transitions.
The matrices $Q_{k}$ and $R_{k}$ define the penalty metric.
Including objectives at each knot point smoothens the optimization landscape, though
the importance of the final state objective is encoded in the relative
weight $Q_{N} \sim N \cdot Q_{k}$.
We choose $Q$ to be diagonal because it is computationally efficient. This corresponds
to penalizing phase differences between the quantum states, although
other phase-insensitive metrics such as infidelity may be employed.

### 2020-11-28 paper/5static.tex
unlimited powah

\section{Robustness to Static Parameter Deviations \label{sec:static}}
We have formulated the quantum optimal control
problem as an open loop optimization problem, i.e.
feedback from the experiment is not incorporated in optimization.
However, the device typically deviates from the Hamiltonian we use in optimization,
leading to poor experimental performance. We combat errors
of this form using robust control techniques,
making the state evolution insensitive
to Hamiltonian parameter deviations. As an example,
we mitigate errors arising from the drift and finite measurement
precision of the qubit frequency in \eqref{eq:hamiltonian}.
We consider three robust control techniques:
the sampling method, the unscented sampling method,
and the derivative method.

The sampling method optimizes over multiple copies of a state,
each of which evolves with a distinct deviant parameter value.
Two samples $\psi_{\pm}$
are appended to the augmented state vector \eqref{eq:astatecontrols}.
for each of four initial states
$\{\ket{0}, \ket{1}, (\ket{0} + i\ket{1}) / \sqrt{2},
(\ket{0} - \ket{1}) / \sqrt{2}\}$. The initial states are chosen
so that their outer products span the operators on the
Hilbert space  \cite{chow2009randomized}.
The discrete dynamics \eqref{eq:dyn_con} is modified so that the
samples evolve under the Hamiltonian given in \eqref{eq:hamiltonian}
with $f_{q} \gets f_{q} \pm \sigma_{f_{q}}$. The final state
for each sample is the image of its initial state
under the desired gate. Deviations from the final state are
penalized in the objective \eqref{eq:costfun}.

For the unscented sampling method, $2(2n + d)$ samples
are appended to the augmented state vector \eqref{eq:astatecontrols}
for each initial state from the operator basis. Here $2n = 4$ is twice the
dimension of the Hilbert space, resulting from the isomorphism \eqref{eq:isomorphism},
and $d = 1$ is the number of deviant parameters. The samples
are used to represent a Gaussian distribution over all $2n$
elements of the initial state, modeling
the uncertainty in the state as a result of the uncertainty in
the deviant parameter. Each sample evolves under the Hamiltonian given in
\eqref{eq:hamiltonian}
where the qubit frequency is replaced by a deviant value determined by the
statistics of the ensemble of samples.
The discrete dynamics \eqref{eq:dyn_con} is modified to 
evolve the samples under the TDSE dynamics \eqref{eq:tdse}
and then apply the unscented transformation to the ensemble,
accurately preserving the first and second moments
of the distribution.
As in the sampling method,
deviations from the final state are penalized according to \eqref{eq:costfun}.
A detailed procedure for the unscented transformation is given
in Appendix \ref{appendix:unscented}.

The derivative method draws on the intuition that
the sensitivity of the state evolution to the deviant parameter
is encoded in the ($l$\textsuperscript{th}-order)
derivative of the state with respect to that parameter
$\partial_{f_{q}}^{l} \psi$. In the $m$\textsuperscript{th}-order
derivative method, all state derivatives of order $1, \dots, m$
are appended to the augmented state vector \eqref{eq:astatecontrols}
for each initial state in the operator basis. The norms of the state derivatives are penalized
in \eqref{eq:costfun} by setting the corresponding final states to zero.
The state derivatives could be obtained in the discrete dynamics \eqref{eq:dyn_con}
with backwards mode differentiation.
Naively applying automatic differentiation
would result in differentiating all dynamics at knot points
$1, \dots, k - 1$ to obtain the state derivative at knot point $k$, requiring
$O(N^{2})$ matrix multiplications. Instead, we 
employ forwards mode differentiation on the TDSE to obtain coupled dynamics
which require $O(N)$ matrix multiplications to integrate.
For example, the dynamics for the $1$\textsuperscript{st}-order derivative method are,
\begin{align}
  i \hbar \frac{d}{dt} \ket{\psi} &= H \ket{\psi}\\
  i \hbar \frac{d}{dt} \ket{\partial_{f_{q}}\psi} &=
  H \ket{\partial_{f_{q}} \psi} +
  (\partial_{f_{q}} H) \ket{\psi}
  \label{eq:d1dyn}
\end{align}
Exponential integrators that account for the non-linear
term in \eqref{eq:d1dyn} may be used to efficiently integrate the coupled dynamics,
see Appendix \ref{appendix:derivative}. For timing results
and an analysis of how the three robust methods scale to larger Hilbert spaces
and more deviant parameters,
consult Appendix \ref{appendix:time}.

To demonstrate the applicability of these techniques
to mitigate parameter deviations,
we consider the task of achieving a single $Z/2$
gate subject to a static qubit frequency detuning
$f_{q} \gets f_{q} + \delta f_{q}$.
We take $\sigma_{f_{q}} / f_{q} = 1\%$ to be one standard devation, and equip
the sampling methods accordingly. For each method we compute the gate error for
one simulated gate application subject to the deviant dynamics given by the
stated qubit frequency detuning $\delta f_{q}$.

We compare the numerical methods
to an analytically derived $Z/2$ gate, see Figure \ref{fig:statica}. 
This gate corresponds to
idling at the flux frustration point $a = 0$. The analytic gate
is at the device's speed limit for a $Z/2$ gate $t_{Z/2} = 1 / 4 f_{q}$ and
is simple to derive. Its erroneous rotation angle $2 \pi t_{Z/2} \delta f_{q}$ is linearly sensitive to
the qubit frequency detuning, resulting in a gate error that is quadratically sensitive
to the qubit frequency detutning.
At a one-percent
qubit frequency detuning the analytic gate achieves a gate error $\sim 4.5 \cdot 10^{-5}$,
which is sufficient for quantum error correction, see Figure \ref{fig:staticb}.
Although the analytic $Z/2$ gate performs well, it works
only at the gate time $t_{Z/2}$. The ability to perform $Z$ rotations in arbitrary times is critical
for operating multi-qubit experiments in the lab frame.
Each numerical method is able to find solutions at
all gate times above $t_{Z/2}$, but is unable to find solutions at shorter times.
These numerical methods offer an effective scheme for synchronizing
qubits operating at different frequencies $f_{q, i} \neq f_{q, j}$.

The sampling and unscented sampling methods
converge on qualitatively similar solutions which combine idling periods
with fast ramps to the maximum amplitude. The gate error at a one-percent
detuning from the nominal qubit frequency achieved
by the sampling method does not improve substantially over the
range of gate durations. The unscented sampling method
achieves linear decreases in its gate error with longer gate durations
until half the larmor period $1 / 2 f_{q}$ after which it achieves a consistent
gate error $\sim 3.5 \cdot 10^{-5}$.

The derivative methods converge on qualitatively similar solutions that
use fast traingle pulses at the boundaries and balance time
on either side of the flux-frustration point symmetrically at low amplitudes.
Both methods achieve a super-linear scaling in their gate error as
a function of the gate duration. The gate error for the 1\textsuperscript{st}-order
derivative method approaches zero at the larmor period $1 / f_{q}$, see Figure \ref{fig:staticc}.
We believe the 1\textsuperscript{st}-order method outperforms the 2\textsuperscript{nd}-order
method due to the low contribution of second-order
terms to the gate error in this deviation regime, see Appendix \ref{appendix:derivative}.
\todo{@Dave should we still make a comment on leaving out the composite
pulse comparison?}

%% Additionally, there are multiple analytic methods 
%% to mitigate errors due to parameter deviations
%% including composite pulse sequences \cite{merrill2014progress},
%% the DRAG scheme \cite{krantz2019quantum}, and
%% geometric phase considerations
%% \cite{xu2020nonadiabatic, han2020experimental}.
%% Composite pulse sequences are derived by computing
%% the erroneous rotation arising from the parameter deviation
%% with a finite order magnus expansion.
%% Pulses are then suitably composed to eliminate the
%% error. In principle the error may be eliminated
%% to arbitrary order with sufficiently many pulses \cite{merrill2014progress},
%% which mirrors the negative correlation between
%% gate error and gate duration we observe with the derivative method.
%% It is difficult to choose an appropriate composite pulse
%% for the problem studied here,
%% so we propose comparisons between composite pulses and numerical techniques
%% for future work.

%% F3
\begin{figure*}[ht]
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3a.png}
    \caption{}
    \label{fig:stochastica}
  \end{subfigure}\hspace{0.025\textwidth}
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3b.png}
        \caption{}
    \label{fig:stochasticb}
  \end{subfigure}
  \caption{
    (a) $X/2$ gates robust to flux offsets constructed with the analytic,
    sampling, unscented sampling, and the 1\textsuperscript{st}-
    and 2\textsuperscript{nd}-order derivative methods. The gates shown
    are the solutions at the analytic gate time.
    (b) Simulation of stochastic 1/$f$ flux noise for
    successive gate applications. The cumulative
    gate error is computed after each gate application.
  }
  \label{fig:stochastic}
\end{figure*}

>>>>

\section{Robustness to Static Parameter Deviations \label{sec:static}}
\todo{standardize gate time vs gate duration} We have formulated the quantum optimal control
problem as an open loop optimization problem, i.e.
feedback from the experiment is not incorporated in optimization.
However, the device typically deviates from the Hamiltonian we use in optimization,
leading to poor experimental performance. We combat errors
of this form using robust control techniques,
making the state evolution insensitive
to Hamiltonian parameter deviations. As an example,
we mitigate errors arising from the drift and finite measurement
precision of the qubit frequency which modifies \eqref{eq:hamiltonian}
by $f_{q} \gets f_{q} + \delta f_{q}$.
We consider three robust control techniques:
the sampling method, the unscented sampling method,
and the derivative method.

The sampling method simultaneously optimizes over copies of a state,
each of which evolves with a distinct deviant parameter value.
A pair of two sample states $\psi_{\pm}$
is appended to the augmented state vector \eqref{eq:astatecontrols}
. The samples are initialized in the same state.
Four pairs
are appended in total corresponding to the initial states
$\{\ket{0}, \ket{1}, (\ket{0} + i\ket{1}) / \sqrt{2},
(\ket{0} - \ket{1}) / \sqrt{2}\}$.
The initial states are chosen
so that their outer products span the operators on the
Hilbert space  \cite{chow2009randomized}.
The discrete dynamics \eqref{eq:dyn_con} is modified so that the
samples evolve under the Hamiltonian given in \eqref{eq:hamiltonian}
with $f_{q} \gets f_{q} \pm \sigma_{f_{q}}$ for a fixed $\sigma_{f_{q}}$.
The final state
for each sample is the image of its initial state
under the desired gate. Deviations from the final state are
penalized in the objective \eqref{eq:costfun}.

For the unscented sampling method, $2(2n + d)$ samples
are appended to the augmented state vector \eqref{eq:astatecontrols}
for each initial state from the operator basis. Here $2n = 4$ is twice the
dimension of the Hilbert space, resulting from the isomorphism \eqref{eq:isomorphism},
and $d = 1$ is the number of deviant parameters. The samples
are used to represent a Gaussian distribution over all $2n$
elements of the initial state, modeling
the uncertainty in the state as a result of the uncertainty in
the deviant parameter. Each sample evolves under the Hamiltonian
given in \eqref{eq:hamiltonian} with $f_{q} \gets f_{q} + \delta f_{q}$.
The qubit frequency detuning $\delta f_{q}$ is determined by the statistics
of the ensemble of samples at each knot point.
The discrete dynamics \eqref{eq:dyn_con} is modified to 
evolve the samples under the deviant Hamiltonian
and then apply the unscented transformation to the ensemble,
accurately preserving the first and second moments
of the distribution.
As in the sampling method,
deviations from the final state are penalized according to \eqref{eq:costfun}.
A detailed procedure for the unscented transformation is given
in Appendix \ref{appendix:unscented}.

The derivative method penalizes the sensitivty of the state
to the deviant parameter, which is encoded in the ($l$\textsuperscript{th}-order)
derivative $\partial_{f_{q}}^{l} \psi$. In the $m$\textsuperscript{th}-order
derivative method, all state derivatives of order $1, \dots, m$
are appended to the augmented state vector \eqref{eq:astatecontrols}
for each initial state in the operator basis.
The norms of the state derivatives are penalized
in \eqref{eq:costfun} by setting the corresponding final states to zero.
The state derivatives could be obtained in the discrete dynamics \eqref{eq:dyn_con}
with backwards mode differentiation.
Naive automatic differentiation
would differentiate all dynamics at knot points
$1, \dots, k - 1$ to obtain the state derivative at knot point $k$, requiring
$O(N^{2})$ matrix multiplications. Instead, we 
employ forwards mode differentiation on the TDSE to obtain coupled dynamics
which require $O(N)$ matrix multiplications to integrate.
For example, the dynamics for the $1$\textsuperscript{st}-order derivative method are,
\begin{align}
  i \hbar \frac{d}{dt} \ket{\psi} &= H \ket{\psi}\\
  i \hbar \frac{d}{dt} \ket{\partial_{f_{q}}\psi} &=
  H \ket{\partial_{f_{q}} \psi} +
  (\partial_{f_{q}} H) \ket{\psi}
  \label{eq:d1dyn}
\end{align}
Exponential integrators that account for the non-linear
term in \eqref{eq:d1dyn} may be used to efficiently integrate the coupled dynamics,
see Appendix \ref{appendix:derivative}. For timing results
and an analysis of how the three robust methods scale to larger Hilbert spaces
and more deviant parameters,
consult Appendix \ref{appendix:time}.

We task these methods with achieving
a $Z/2$ gate subject to a static qubit frequency detuning.
We take $\sigma_{f_{q}} / f_{q} = 1\%$ to be one standard devation, and equip
the sampling methods accordingly. We compute gate errors for each method
by evolving the optimized trajectory under the Hamiltonian in \eqref{eq:hamiltonain}
with $f_{q} \gets f_{q} + \delta f_{q}$ at the stated qubit frequency detuning.

We compare the numerical methods
to an analytically derived $Z/2$ gate, see Figure \ref{fig:statica}. 
The analytic gate corresponds to
idling at the flux frustration point $a = 0$. It
is at the device's speed limit for a $Z/2$ gate $t_{Z/2} = 1 / 4 f_{q}$ and
is simple to derive. Its erroneous rotation angle $2 \pi t_{Z/2} \delta f_{q}$ is linearly sensitive to
the qubit frequency detuning, resulting in a gate error that is quadratically sensitive
to the qubit frequency detutning.
At a one-percent
qubit frequency detuning ($\delta f_{q} / f_{q} = 1\%$)
the analytic gate achieves a gate error $\sim 4.5 \cdot 10^{-5}$,
which is sufficient for quantum error correction.
Although the analytic $Z/2$ gate performs well, it
only works at the gate time $t_{Z/2}$. The ability to perform $Z$ rotations in arbitrary times is critical
for multi-qubit experiments, where the qubits operate at different frequencies $f_{q, i} \neq f_{q, j}$.
Each numerical method is able to find solutions at
all gate times above $t_{Z/2}$, see Figure \ref{fig:staticb}.
These numerical methods offer an effective scheme for synchronizing
multi-qubit experiments.

The sampling and unscented sampling methods combine idling periods
with time-anti-symmetric ramps.
The gate error at $\delta f_{q} / f_{q} = 1\%$ for the sampling method
does not improve substantially over the
range of gate durations. The unscented sampling method
achieves linear decreases in its gate error at $\delta f_{q} / f_{q} = 1\%$ with longer gate durations
until half the larmor period $1 / 2 f_{q}$ after which it achieves a consistent
gate error $\sim 3.5 \cdot 10^{-5}$.

The derivative methods converge on qualitatively similar solutions that
use fast traingle pulses at the boundaries and balance time
on either side of the flux-frustration point symmetrically at low amplitudes.
Both methods achieve a super-linear scaling in their gate error as
a function of the gate duration. The gate error for the 1\textsuperscript{st}-order
derivative method approaches zero at the larmor period $1 / f_{q}$, see Figure \ref{fig:staticc}.
We believe the 1\textsuperscript{st}-order method outperforms the 2\textsuperscript{nd}-order
method due to the low contribution of second-order
terms to the gate error in this deviation regime, see Appendix \ref{appendix:derivative}.
The vanishing gate error at longer gate durations exhibited by the derivative methods
is reminiscent of the
ability of composite pulses to mitigate parameter deviation errors to arbitrary
order with sufficiently many pulses \cite{merrill2014progress}.
It is difficult to choose an appropriate composite pulse
for the problem studied here due to our Hamiltonian and experimental constraints.
We propose comparisons between composite pulses and numerical techniques
for future work.

%% F3
\begin{figure*}[ht]
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3a.png}
    \caption{}
    \label{fig:stochastica}
  \end{subfigure}\hspace{0.025\textwidth}
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3b.png}
        \caption{}
    \label{fig:stochasticb}
  \end{subfigure}
  \caption{
    \todo{fix the size of the images and where are x axis labels?}
    (a) $X/2$ gates robust to flux offsets constructed with the analytic,
    sampling, unscented sampling, and the 1\textsuperscript{st}-
    and 2\textsuperscript{nd}-order derivative methods. The gates shown
    are the solutions at the analytic gate time.
    (b) Simulation of stochastic 1/$f$ flux noise for
    successive gate applications. The cumulative
    gate error is computed after each gate application.
  }
  \label{fig:stochastic}
\end{figure*}

### 2020-11-28 paper/6stochastic.tex
unlimited powah

\section{Robustness to Time-Dependent Parameter Deviations \label{sec:stochastic}}
An additional source of experimental error arises from time-dependent
Hamiltonian parameter deviations. For many flux-biased and inductively-coupled
superconducting circuit elements, magnetic flux noise is a significant
source of coherent errors. Magnetic flux noise
modifies the fluxonium qubit's amplitude from its nominal value by an amount $\delta a(t)$.
It is well studied that the spectral density of $\delta a(t)$ follows a
1/$f$ distribution for a range of devices, consisting primarily of low frequency
noise \todo{1/$f$ citations}. Analytic methods to combat flux noise
take advantage of the low frequency characteristic and
treat the noise as quasi-static, performing generalizations of the spin-echo technique
to compensate for erroneous drift. This is the strategy employed by the analytic gate
considered here.

We compare the analytic gate and those produced by
the numerical methods discussed in the previous section
on the task of realizing a $X/2$ gate subject to 1/$f$ flux noise.
The flux noise is generated by
filtering white noise sampled from a standard normal distribution with a finite
impulse response filter \cite{saspweb2011}.
It is then scaled by the 
flux noise amplitude of our device $A_{\Phi} = 5.21 \mu \Phi_{0} \implies
\delta a \sim 2.5 \cdot 10^{-5} \textrm{GHz}$. This filtered noise
is then used to evolve the state under the Hamiltonian in \eqref{eq:hamiltonian}
with the flux amplitude replaced $a(t) \gets a(t) + \delta a(t)$.
The unscented sampling method is modified so that its sampled deviations
follow a 1/$f$ distribution by carrying the state of a finite impulse response filter
in the augmented state vector. In principle the basic sampling method could be modified
similarly but we choose to sample statically at $\delta a$ for comparision. The derivative
methods require no modification from the static case.
\todo{can you provide a little more 
detail on how this noise factors into the dynamics? Are you just adding some white 
noise to $a(t)$? Are you also considering uncertainty in $f_q$ at the same time?}

>>>>

\section{Robustness to Time-Dependent Parameter Deviations \label{sec:stochastic}}
An additional source of experimental error arises from time-dependent
Hamiltonian parameter deviations. For many flux-biased and inductively-coupled
superconducting circuit elements, magnetic flux noise is a significant
source of coherent errors. Magnetic flux noise
modifies the fluxonium Hamiltonian \eqref{eq:hamiltonian}
by $a(t) \gets a(t) + \delta a(t)$.
It is well studied that the spectral density of $\delta a(t)$ follows a
1/$f$ distribution for a range of devices, consisting primarily of low frequency
noise \todo{1/$f$ citations}. Analytic methods to combat flux noise
take advantage of the low frequency characteristic and
treat the noise as quasi-static, performing generalizations of the spin-echo technique
to compensate for erroneous drift. This is the strategy employed by the analytic gate
considered here.

We task the analytic gate and those produced by
the robust control methods of the previous section
to realize an $X/2$ gate subject to 1/$f$ flux noise.
We compute gate errors for each method
by evolving the optimized trajectory under the Hamiltonian in \eqref{eq:hamiltonain}
with $a(t) \gets a(t) + \delta a(t)$.
The flux noise $\delta a(t)$ is generated by
filtering white noise sampled from a standard normal distribution with a finite
impulse response filter \cite{saspweb2011}.
It is then scaled by the 
flux noise amplitude of our device $A_{\Phi} = 5.21 \mu \Phi_{0} \implies
\delta a (t) \sim \sigma_{a} = 2.5 \cdot 10^{-5} \textrm{GHz}$.
The unscented sampling method is modified so that its samples
are subject to 1/$f$ flux noise by carrying the state of a finite impulse response filter
in the augmented state vector \eqref{eq:astatecontrols}.
In principle the sampling method could be modified
similarly but we choose to sample statically at $\sigma_{a}$ for comparision.
The derivative methods require no algorithmic modification from the static case,
but the TDSE is now differentiated with respect to $a(t)$ instead of $f_{q}$ as
in \eqref{d1dyn}.

### 2020-11-28 paper/8ack.tex
full build
unlimited powah

%% ACK
\begin{acknowledgments}
  The authors would like to thank Helin Zhang for experimental assistance
  and Daniel Weiss for useful discussions.
\end{acknowledgments}

>>>>

\begin{acknowledgments}
  The authors would like to thank Helin Zhang for experimental assistance
  and Daniel Weiss, Taylor Howell, and Tanay Roy for useful discussions. \todo{cite software packages}.
  \todo{funding}.
\end{acknowledgments}
